Energy and the CES production function

### 2015-07-10 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Improving readability of lambda vs. mse graph.

>>>>

<<SRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($mse$). $\\lambda$ and $mse$ values for the reference (exponential-only) model are shown as gridlines.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=mse, y=lambda, color=energy, size=cst, shape=nest)) +
  geom_vline(aes(xintercept = mse), filter(AllCoeffs, model=="exp") %>% select(Country, mse), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = lambda), filter(AllCoeffs, model=="exp") %>% select(Country, lambda), colour="gray50", size=0.1) +
  scale_size_manual(values=c(2,4)) +
  scale_shape_manual(values=c(1,0,3,4)) + # 16,17,18,15
  facet_grid(Country ~ flavor) +
  # scale_x_continuous(breaks=seq(0, 0.02, 0.01), limits=c(0, 0.02)) +  
  ylab(expression(lambda)) +
  # scale_y_continuous(breaks=seq(0, 0.04, 0.01), limits=c(0, 0.04)) +  
  xy_theme() +
  theme(legend.title=element_blank())
@
